Placeholder Title... Something About Delegating Quantum Computations

### 2019-10-15 longoutput.tex
Fix overfull hbox
Add TODO to clarify output subsection
Change TODOs to note macros
Fix typo
Rename procedure

\begin{proof}
	We construct the Hamiltonian by ensuring states perpendicular to $\ket{\psi_{circuit}}$ have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.

@@

	\begin{proof}
		Let $\ket\phi\in K_{clock}\cap K_{prop}$. As $\ket\phi\in K_{clock}$, the time register components are always valid unary representations. Now consider some $\widetilde{t}$ such that $\bra{\widetilde{t}}\ket\phi\ne0$. As $\ket\phi\in K_{prop}$, we can then say that $\bra{\widetilde{t+1}}\ket\phi=\bra{\widetilde{t}}U_{t+1}\ket\phi$ for $t\ne T$, and $\bra{\widetilde{t}}\ket\phi=U_t\bra{\widetilde{t-1}}\ket\phi$ for $t\ne0$. So we can obtain the required statement by induction.
	\end{proof}

@@

Let $\varepsilon>0$, $p>0$. Pick $n\in\mathbb{N}$ so that by Chernoff bound:
\begin{itemize}
	\item $\ket{\psi^{\otimes n}}$ is rejected with probability at most $1-p$.
	\item If $\mathcal{F}(\ket{\phi})$ has less than $\frac{1}{2}-\varepsilon$ accept probability, then $\ket{\phi^{\otimes n}}$ is accepted with probability at most $p$.
\end{itemize}

\begin{algorithm}
	\caption{Amplification with simple input}
	\label{AlgAmp1}
	\begin{algorithmic}[1]
		\Require $\phi=\sum_i w_i\ket{\rho_i^{\otimes n+m}}\bra{\rho_i^{\otimes n+m}}$
		\Procedure{SimpleAmplification}{$\phi$}
		\State Apply $\mathcal{F}$ to first $n$ registers of $\phi$
		\If{number of accepted copies $\geq \frac{1}{2}-\varepsilon$}
			\State Output the last $m$ registers
		\Else
			\State Reject
		\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

>>>>

\begin{proof}
	We ensure states perpendicular to $\ket{\psi_{circuit}}$ have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.

@@

	\begin{proof}
		Let $\ket\phi\in K_{clock}\cap K_{prop}$. As $\ket\phi\in K_{clock}$, the time register components are always valid unary representations. Now consider some $\widetilde{t}$ such that $\braket{\widetilde{t}|\phi}\ne0$. As $\ket\phi\in K_{prop}$, we can then say that $\bra{\widetilde{t+1}}\ket\phi=\bra{\widetilde{t}}U_{t+1}\ket\phi$ for $t\ne T$, and $\bra{\widetilde{t}}\ket\phi=U_t\bra{\widetilde{t-1}}\ket\phi$ for $t\ne0$. So we can obtain the required statement by induction.
	\end{proof}

@@

Let $\varepsilon>0$, $p>0$. Pick $n\in\mathbb{N}$ so that by Chernoff bound:
\begin{itemize}
	\item $\ket{\psi^{\otimes n}}$ is rejected with probability at most $p$.
	\item If $\mathcal{F}(\ket{\phi})$ has less than $\frac{1}{2}-\varepsilon$ accept probability, then $\ket{\phi^{\otimes n}}$ is accepted with probability at most $p$.
\end{itemize}

\begin{algorithm}
	\caption{Amplification with simple input}
	\label{AlgAmp1}
	\begin{algorithmic}[1]
		\Require $\phi=\sum_i w_i\ket{\rho_i^{\otimes n+m}}\bra{\rho_i^{\otimes n+m}}$
		\Procedure{Amplification}{$\phi$}
		\State Apply $\mathcal{F}$ to first $n$ registers of $\phi$
		\If{number of accepted copies $\geq \frac{1}{2}-\varepsilon$}
			\State Output the last $m$ registers
		\Else
			\State Reject
		\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

\Ethan{The above is incredibly handwavy.}
